On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-11-25 paper/paper.tex
'standard semantics' -> 'reference semantics'

\begin{itemize}
  \item A representation of pattern matching in a Haskell EDSL (Section~\ref{sec:PatRep})
  \item A representation of lambdas (Section~\ref{sec:LamRep}) in the EDSL, utilizing
  the fact that both pattern matching and tail recursion are already captured in
  the EDSL.
  \item A GHC Core plugin which transforms a subset of standard Haskell code
  into this EDSL for pattern matching, extended with tail recursion,
  lambdas and primitive operations (Section~\ref{sec:CorePlugin})
  \item An implementation of an interpreter for the ``standard'' semantics of the EDSL (Section~\ref{sec:StdSemantics}).
% \item An outline of a C backend for this EDSL (Section~\ref{sec:CBackend}).
\end{itemize}

@@

The function \ttt{runIter} provides the standard semantics for executing such a
function representing a tail recursive function:

@@

\section{Recovering standard semantics for pattern matches}
\label{sec:StdSemantics}

The standard semantics for the EDSL is given by \ttt{abs}. Two helper
functions, \ttt{sumMatchAbs} and \ttt{prodMatchAbs}, are used to provide
the standard semantics for matches on sum types and matches on product
types, respectively. These helper functions are based on the mechanism
described in Section~\ref{sec:MatchAside}.

>>>>

\begin{itemize}
  \item A representation of pattern matching in a Haskell EDSL (Section~\ref{sec:PatRep})
  \item A representation of lambdas (Section~\ref{sec:LamRep}) in the EDSL, utilizing
  the fact that both pattern matching and tail recursion are already captured in
  the EDSL.
  \item A GHC Core plugin which transforms a subset of standard Haskell code
  into this EDSL for pattern matching, extended with tail recursion,
  lambdas and primitive operations (Section~\ref{sec:CorePlugin})
  \item An implementation of an interpreter for a reference semantics of the EDSL (Section~\ref{sec:StdSemantics}).
% \item An outline of a C backend for this EDSL (Section~\ref{sec:CBackend}).
\end{itemize}

@@

The function \ttt{runIter} provides the reference semantics for executing such a
function representing a tail recursive function:

@@

\section{Recovering reference semantics for pattern matches}
\label{sec:StdSemantics}

The reference semantics for the EDSL is given by \ttt{abs}. Two helper
functions, \ttt{sumMatchAbs} and \ttt{prodMatchAbs}, are used to provide
the reference semantics for matches on sum types and matches on product
types, respectively. These helper functions are based on the mechanism
described in Section~\ref{sec:MatchAside}.
